Matrix completion and semidefinite matrices

### 2021-12-01 paper/paper_math.tex
Fixed bibliography

\begin{thebibliography}{MM}
	\bibitem{grone} R. Grone, C. R. Johnson, E. Sa, H. Wolkowicz, Positive definite completions of partial Hermitian matrices, Linear Algebra Appl. 58 (1984) 109-124.
	\bibitem{smith} Smith, R. (2008). The positive definite completion problem revisited Linear Algebra and its Applications  429(7), 1442-1452. https://dx.doi.org/10.1016/j.laa.2008.04.020
	\bibitem{golumbic} M.C. Golumbic, W. Rheinboldt, Algorithmic Graph Theory and Perfect Graphs, 1st edition, Elsevier Inc, Academic Press, 1980.
	\bibitem{roger} Penrose, R. (1955). A generalized inverse for matrices Mathematical Proceedings of the Cambridge Philosophical Society  51(3), 406-413. https://dx.doi.org/10.1017/s0305004100030401
	\bibitem{matrixanalysis} Roger A. Horn, Charles R. Johnson, \emph{Matrix Analysis}, 2nd Edition, Cambridge University Press, 2013.
	\bibitem{hayns} Emilie Virginia Haynsworth, Determination of the inertia of a partitioned Hermitian matrix,  Linear  Algebra and its Applications \textbf{1}, 1968, 73--81.
	\bibitem{horn} Roger A. Horn, Basic  Properties  of  the  Schur  Complement. In Fuzhen Zhang (Ed.) The Schur complement and its application (17--46). Springer, 2005.
	\bibitem{schur} J. Schur, Über Potenzreihen, die im Innern des Einheitskreises beschränkt sind, Journal für die reine und angewandte Mathematik \textbf{147}, 205 -- 232, 1917.
	\bibitem{bana} T. Banachiewicz, Zur Berechnung der Determinanten, wie auch der Inversen, und zur darauf basierten Auflösung der Systeme linearer Gleichungen, Acta Astronom. S\'er. C 3, 41--67, 1937.
	\bibitem{frazer} Frazer, R., Duncan, W., Collar, A. (1938). Elementary Matrices And Some Applications To Dynamics And Differential Equations, Cambridge University Press, 1938.
	\bibitem{ouellette} Ouellette, D. (1981). Schur complements and statistics Linear Algebra and its Applications  36, 187-295. https://dx.doi.org/10.1016/0024-3795(81)90232-9
	\bibitem{albert} Albert, A. (1969). Conditions for Positive and Nonnegative Definiteness in Terms of Pseudoinverses SIAM Journal on Applied Mathematics  17(2), 434-440. https://dx.doi.org/10.1137/0117041
	\bibitem{otherpaper} O. Dreyer, H. Köhler, T. Streuer, Completing correlation matrices, arXiv:2111.12640 
\end{thebibliography}

>>>>

\begin{thebibliography}{MM}
	\bibitem{grone} R. Grone, C. R. Johnson, E. Sa, H. Wolkowicz, Positive definite completions of partial Hermitian matrices, Linear Algebra Appl. 58 (1984) 109--124. https://doi.org/10.1016/0024-3795(84)90207-6.
	\bibitem{smith} R. L. Smith, The positive definite completion problem revisited, Linear Algebra Appl. 429 (2008) 1442--1452. https://dx.doi.org/10.1016/j.laa.2008.04.020
	\bibitem{golumbic} M.C. Golumbic, W. Rheinboldt, Algorithmic Graph Theory and Perfect Graphs, 1st edition, Elsevier Inc, Academic Press, 1980.
	\bibitem{roger} R. Penrose, A generalized inverse for matrices, Math Proc Cambridge 51 (1955) 406--413. https://doi.org/10.1017/s0305004100030401.
	\bibitem{matrixanalysis} R. A. Horn, C. R. Johnson, Matrix Analysis, 2nd ed., Cambridge University Press, 2012.
	\bibitem{hayns} E. V. Haynsworth, Determination of the inertia of a partitioned Hermitian matrix,  Linear Algebra Appl. 1 (1968) 73--81.
	\bibitem{horn} R. A. Horn, Basic  Properties  of  the  Schur  Complement. In Fuzhen Zhang (Ed.), The Schur complement and its application (17--46), Springer, 2005.
	\bibitem{schur} J. Schur, Über Potenzreihen, die im Innern des Einheitskreises beschränkt sind, Journal für die reine und angewandte Mathematik 147 (1917) 205 -- 232.
	\bibitem{bana} T. Banachiewicz, Zur Berechnung der Determinanten, wie auch der Inversen, und zur darauf basierten Auflösung der Systeme linearer Gleichungen, Acta Astronom. S\'er. C 3 (1937) 41--67.	
	\bibitem{frazer} R. Frazer, W. Duncan, A. Collar, Elementary Matrices And Some Applications To Dynamics And Differential Equations, Cambridge University Press, 1938.
	\bibitem{ouellette} D. Ouellette, Schur complements and statistics Linear Algebra Appl. 36 (1981) 187--295. https://dx.doi.org/10.1016/0024-3795(81)90232-9.
	\bibitem{albert} A. Albert, Conditions for Positive and Nonnegative Definiteness in Terms of Pseudoinverses, SIAM Journal on Applied Mathematics  17 (1969) 434--440. https://dx.doi.org/10.1137/0117041
	\bibitem{otherpaper} O. Dreyer, H. Köhler, T. Streuer, Completing correlation matrices, arXiv:2111.12640 
\end{thebibliography}
